Wealth dynamics in the presence of network structure and primitive cooperation

### 2019-07-12 manuscript/draftcssa19.tex
Begin implementation section.

\subsection{Implementation}
%Stephen thinks that a subsection of the Model section should be about the
%simulation code. It won't be long; just enough to explain how the mathematical
%model just described is represented and executed in Julia, including some
%answers to non-obvious questions that arise when considering implementation.

>>>>

\subsection{Implementation}

The model is realized in a discrete-time Julia simulation program, in which each particle (agent) is represented as a mutable struct that maintains that agent's state over time. Each agent's state includes its current amount of wealth and which proto (if any) it is a member of. Additionally, using the LightGraphs package~\cite{LightGraphs-2017}, each agent is associated with a node of a randomly generated ER graph. Protos are also represented as mutable structs, each of which contains a list of member agent IDs and a current wealth balance.

% cite Bootstrap?
We chose Julia for its flexible type system, its speed of execution, its ease of programming, and the availability of useful packages, such as LightGraphs, Gadfly~\cite{Gadfly-2018} (plotting), and Bootstrap (confidence intervals).  Additionally, Julia easily allows the programmer to invoke code from R packages when necessary, as we did for Gini coefficient calculation with the R package DescTools~\cite{DescTools-2019}.
